### 2012-12-19 inst/examples/reed-example.Rmd
Parameteric Ricker model underestimates growth and thus underperforms relative to BH (true) or GP

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "bevholt-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

>>>>

```{r set-options, include=FALSE, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "bevholt-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

Simulate data
